%-------------------------
% Résumé / CV - Yann COTINEAU
% Version : 1.0.0 - 2026-03 (EN)
% Based off of: https://github.com/jakegut/resume
% License: MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

%---- Page style ----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%---- Margins ----
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%---- Section formatting ----
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%---- ATS parsability ----
\pdfgentounicode=1

%---- Custom commands ----
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%  RESUME STARTS HERE
%-------------------------------------------

\begin{document}

%---- Heading ----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Huge Yann Cotineau} &
    \begin{tabular}[c]{r}
        \small \faEnvelope\ \href{mailto:yanncotineau@gmail.com}{yanncotineau@gmail.com} \\
        \small \faPhone\ +33\,6\,60\,43\,56\,34
    \end{tabular}
\end{tabular*}

\begin{center}
    \small
    \faGithub\ \href{https://github.com/yanncotineau}{github.com/yanncotineau} $|$
    \faGlobe\ \href{https://yanncotineau.dev}{yanncotineau.dev} $|$
    \faLinkedin\ \href{https://linkedin.com/in/yanncotineau}{linkedin.com/in/yanncotineau}
\end{center}

Full stack software engineer passionate about AI. I design, develop and ship modern, robust applications, with a constant focus on quality, architectural best practices and continuous deployment. Open to new opportunities.

%---- Experience ----
\section{Professional Experience}
    \resumeSubHeadingListStart

        \resumeSubheading
            {Software Developer}{June 2024 -- Present}
            {IMATECH, Groupe IMA}{Nantes, France}
            \resumeItemListStart
                \resumeItem{Developed a legal \textbf{RAG} solution with AI agents (\textbf{LangChain}, \textbf{LangGraph}), \textbf{Fastify} backend and \textbf{React} frontend, powered by internal legal documents, used by 150 in-house lawyers and commercialized.}
                \resumeItem{Designed and implemented a modular, configurable microservices architecture (\textbf{Node.js} / \textbf{Fastify}) for incremental document vectorization (\textbf{RAG}), significantly reducing inference costs.}
                \resumeItem{Led the complete overhaul of legacy applications to modern full-stack architectures (\textbf{Java Spring Boot} / \textbf{React}): improved \textbf{UI/UX} with a responsive \textbf{Ant Design} interface and strengthened security via \textbf{SSO}.}
                \resumeItem{Contributed to the maintenance and evolution of internal CRM applications (\textbf{Java Spring Boot}, \textbf{Ext.js}): feature development, unit testing, documentation, in an \textbf{Agile} team with 2-week sprints.}
                \resumeItem{Set up \textbf{CI/CD} pipelines, containerization and deployment on \textbf{Kubernetes} via \textbf{Azure DevOps}.}
                \resumeItem{Collaborated closely with business teams to refine requirements and continuously optimize \textbf{UI/UX}.}
            \resumeItemListEnd

        \resumeSubheading
            {Web Developer}{Aug. 2023 -- Dec. 2023}
            {8P Design}{Montréal, QC}
            \resumeItemListStart
                \resumeItem{Developed a full-stack \textbf{RAG} application (\textbf{Drupal 10}, \textbf{Vue.js}) with Pinecone and OpenAI's API (GPT-4) to automate client interactions and report generation. Continuous deployment via \textbf{GitLab CI/CD}.}
                \resumeItem{Improved internal \textbf{CI/CD} processes (dev/staging/prod) with local \textbf{containerization} and automated deployment. Wrote documentation to facilitate collaboration and onboarding of new developers.}
                \resumeItem{Maintained and improved client websites in production (\textbf{PHP}, \textbf{Drupal}, \textbf{Wordpress}): bug fixes, adjustments based on user feedback and regular deployments.}
                \resumeItem{Conducted technology watch on new AI capabilities to enrich services offered to clients.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd

%---- Education ----
\section{Education}
    \resumeSubHeadingListStart

        \resumeSubheading
            {Université du Québec à Chicoutimi}{Saguenay, QC}
            {Master's in Computer Science (professional)}
            {Aug. 2022 -- Jan. 2024}
        \vspace{2pt}

        \resumeSubheading
            {ENSISA}{Mulhouse, France}
            {Computer Science \& Networks Engineering (dual degree France/Québec)}
            {Sep. 2020 -- Jan. 2024}
        \vspace{2pt}

        \resumeSubheading
            {Lycée Henri Bergson}{Angers, France}
            {Preparatory Classes for Engineering Schools (Mathematics-Physics-Engineering Sciences)}
            {Sep. 2018 -- July 2020}

    \resumeSubHeadingListEnd

%---- Projects ----
\section{Projects}
    \resumeSubHeadingListStart

        \resumeProjectHeading
            {\textbf{LichessTrends} $|$ \emph{Rust, Next.js, React, TypeScript, GitHub Actions, Vercel}}{\href{https://lichesstrends.com}{\textbf{lichesstrends.com}}}
            \resumeItemListStart
                \resumeItem{Developed a high-performance aggregator in \textbf{Rust} for streaming processing of 100M+ monthly chess games from \textbf{Lichess} (online chess platform), generating actionable aggregated statistics.}
                \resumeItem{Designed a \textbf{Next.js} / \textbf{React} application exposing a \textbf{REST API}, with interactive visualizations (\textbf{Recharts}, \textbf{TanStack Query}) to explore these statistics (games, ratings, popular openings, etc.).}
                \resumeItem{Deployed the application on \textbf{Vercel} with server-side caching to speed up queries. Automated monthly ingestion of new Lichess data via a \textbf{GitHub Actions} workflow.}
            \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{Blog \& Portfolio Website} $|$ \emph{Next.js, React, TypeScript, MDX, GitHub Actions, Vercel}}{\href{https://yanncotineau.dev}{\textbf{yanncotineau.dev}}}
            \resumeItemListStart
                \resumeItem{Designed my blog in 2 parts: \textbf{MDX} articles versioned in a dedicated \textbf{Git} repo, transformed into static pages by a custom \textbf{Next.js} CMS (\textbf{Contentlayer}) with interactive \textbf{React} components embedded in the content.}
                \resumeItem{Automatic redeployment of the blog via \textbf{GitHub Actions} and \textbf{Vercel} deploy hook on every article change, with per-file \textbf{Git} metadata extraction (commit, date, diff) displayed on each article.}
                \resumeItem{Developed a portfolio website in \textbf{Next.js} / \textbf{React} showcasing my background, skills, experience and projects, fetching the latest blog articles via \textbf{REST API}. Deployed on \textbf{Vercel}.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd

%---- Skills ----
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
            \textbf{Languages} : Java, TypeScript, JavaScript, Python, SQL, PHP, HTML/CSS \\
            \textbf{Frontend} : React, Vue.js, Next.js, Vitest, TanStack Query, Ant Design, MUI \\
            \textbf{Backend} : Spring Boot, Express, FastAPI, Liquibase, Fastify, Node.js, JUnit, Jest \\
            \textbf{AI \& LLMs} : LangChain, LangGraph, Prompt Engineering, RAG, Agentic RAG, Ollama, Pinecone, Qdrant \\
            \textbf{DevOps \& CI/CD} : Docker, Kubernetes, Azure DevOps, Harbor, GitHub Actions, Renovate, Nexus \\
            \textbf{Tools} : Git, GitHub, VS Code, IntelliJ, Postman, WSL, GitHub Copilot, Figma \\
            \textbf{Methods} : Agile Development, GitFlow, Scrum
        }}
    \end{itemize}

%---- Languages ----
\section{Languages}
    \textbf{French} (native), \textbf{English} (fluent/professional, C1)

%-------------------------------------------
\end{document}